### 2012-08-10 inst/doc/policycosts/policycosts.tex
policycosts compare against Reed under cost reality

\subsection{Apples to Apples comparisons: Calibraring the magnitude of the penalty coefficient}

We compare the impact of the different functional forms for the penalty
function at a value of the penalty scaling parameter in each model that
induces an equivalent net present value to the stock when optimally
managed under this penalty. This value represents the expected net
present value before the costs of policy adjustment are paid.

  \begin{figure}
    \begin{center}
\includegraphics[width=.8\textwidth]{figure/7258601130_c2fc0bcfa4_o.png}
\caption{\textbf{Net present value} We compare the impact of the different functional forms for the penalty
function at a value of the penalty scaling parameter in each model that
induces an equivalent net present value to the stock when optimally
managed under this penalty. This value represents the expected net
present value before the costs of policy adjustment are paid.}
\end{center}
\end{figure}

@@

  \begin{figure}
    \begin{center}
 \includegraphics[width=.8\textwidth]{figure/7258516896_5c89f034d5_o.png}
 \caption{L1 example}
  \end{center}
\end{figure}

  \begin{figure}
    \begin{center}
 \includegraphics[width=.8\textwidth]{figure/7258563112_2f5f9ffecd_o.png}
  \end{center}
 \caption{L2 example}
\end{figure}

  \begin{figure}
    \begin{center}
 \includegraphics[width=.8\textwidth]{figure/7258506664_d6235e5f8e_o.png}
  \end{center}
 \caption{Fixed Fee example}
\end{figure}

  \begin{figure}
    \begin{center}
 \includegraphics[width=.8\textwidth]{figure/7258432026_d6f8179f54_o.png}
  \end{center}
 \caption{Asymmetric costs example}
\end{figure}

@@

  \begin{figure}
    \begin{center}
    \includegraphics[width=.8\textwidth]{figure/6850042286_ef81b74acc_o.png}
    \caption{Variance vs magnitude of penalty, by penalty function}
  \end{center}
\end{figure}
  \begin{figure}
    \begin{center}
   \includegraphics[width=.8\textwidth]{figure/6996165783_41c9894bdb_o.png}
    \caption{autocorrelation vs magnitude of penalty, by penalty function}
  \end{center}
\end{figure}

>>>>

\subsection{Apples to apples comparisons}

We compare the impact of the different functional forms for the penalty
function at a value of the penalty scaling parameter in each model that
induces an equivalent net present value to the stock when optimally
managed under this penalty. This value represents the expected net
present value before the costs of policy adjustment are paid, Figure~\ref{fig:apples}

  \begin{figure}
    \begin{center}
\includegraphics[width=.8\textwidth]{figure/7258601130_c2fc0bcfa4_o.png}
\caption{\textbf{Net present value} We compare the impact of the different functional forms for the penalty
function at a value of the penalty scaling parameter in each model that
induces an equivalent net present value to the stock when optimally
managed under this penalty. This value represents the expected net
present value before the costs of policy adjustment are paid.}
\label{fig:apples}
\end{center}
\end{figure}

@@

  \begin{figure}
    \begin{center}
      \subfigure[$L_1$]{\includegraphics[width=.45\textwidth]{figure/7258516896_5c89f034d5_o.png}\label{fig:L1}}
      \subfigure[$L_2$]{\includegraphics[width=.45\textwidth]{figure/7258563112_2f5f9ffecd_o.png}\label{fig:L2}}

      \subfigure[Fixed costs]{\includegraphics[width=.45\textwidth]{figure/7258506664_d6235e5f8e_o.png}\label{fig:fixed}}
      \subfigure[Asymmetric costs]{\includegraphics[width=.45\textwidth]{figure/7258432026_d6f8179f54_o.png}\label{fig:asym}}
  \end{center}
 \caption{Individual realizations of management under each stochastic cost}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \subfigure[Variance]{\includegraphics[width=.45\textwidth]{figure/6850042286_ef81b74acc_o.png}\label{fig:var}}
    \subfigure[Autocorrelation]{\includegraphics[width=.45\textwidth]{figure/6996165783_41c9894bdb_o.png}\label{fig:acor}}
    \caption{Variance and autocorrelation as a function of the magnitude of penalty, by penalty function}
  \end{center}
\end{figure}

### 2012-08-10 inst/examples/policycosts/L1.Rmd
policycosts compare against Reed under cost reality

`ro fig.width=10, fig.height=7, message=FALSE, comment=NA, cache=TRUE, verbose=TRUE, cache.path="L1/" or`

@@

``` {r policycost_optim }
c2 <- 1.52
penalty <- L1(c2)
policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                    profit, delta, reward, penalty = penalty)
````

@@

``` {r policycost}
costs <- dt[ , sum(policy_cost * (1-delta)^(time-1)), by=reps]
profits <-dt[ , sum(profit_fishing * (1-delta)^(time-1)), by=reps]

qplot(costs$V1)
qplot(profits$V1)
qplot(profits$V1-costs$V1)
````

@@

```{r}
mean(profits$V1)
sd(profits$V1)
````

Compare these induced costs to the costs of actual adjustment.  Direct costs:

```{r}
mean(costs$V1)
sd(costs$V1)
````

Induced costs:

```{r}
380.4 - mean(profits$V1)
````

>>>>

`ro fig.width=10, fig.height=7, message=FALSE, comment=NA, cache=FALSE, verbose=TRUE, cache.path="L1/" or`

@@

``` {r policycost_optim }
c2 <- 4 #1.52 is calculated to match, but try bigger!
penalty <- L1(c2)
policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                    profit, delta, reward, penalty = penalty)
````

@@

``` {r policycost}
costs <- dt[, sum(policy_cost * (1 - delta)^(time - 1)), by = reps]$V1
profits <- dt[, sum(profit_fishing * (1 - delta)^(time - 1)), by = reps]$V1
costs_alt <- dt[, sum(policy_cost_alt * (1 - delta)^(time - 1)), by = reps]$V1
profits_alt <- dt[, sum(profit_fishing_alt * (1 - delta)^(time - 1)), by = reps]$V1

qplot(costs)
qplot(profits)
qplot(profits-costs)
````

@@

```{r}
mean(profits)-mean(costs)
mean(profits_alt) - mean(costs_alt)

values <- data.frame(profits= profits, costs=costs, naiive_profit = profits_alt, naiive_costs = costs_alt)
ggplot(melt(values)) + geom_density(aes(value, fill=variable), alpha=.7) + theme_bw()

npv <- data.frame(policywise = profits-costs, naiive = profits_alt - costs_alt)
ggplot(melt(npv)) + geom_density(aes(value, fill=variable), alpha=.7) + theme_bw()
````
